US General Society Survey Analysis

### 2024-03-17 paper/paper.qmd
.

Lastly, we will look at @fig-trump2020 which is essentially the invers of the previous graph as there were no other possible data points other than "Biden" and "Trump"

>>>>

Lastly, we will look at @fig-trump2020 which is essentially the inverse of the previous graph as there were no other possible data points other than "Biden" and "Trump". While this graph may just be a reflection across the 50% line, it is still helpful so that wer may look at it from a different perspective. Just as in @fig-biden2020, @fig-trump2020 has a small peak after the year 1950. It is also important to note that even though there is a peak after the year 1950, all of the ages that had more than a 50% vote share for trump all also came before the year 1950.
